\section{Analysis}
\label{sec:analysis}

\paragraph{Pre-screening, calibration, and deployment PPV.}
\label{sec:prescreening}
\label{sec:calibration}
\label{sec:ppv}
The optional pre-screening layer (DOI format, year-range bounds, author-name heuristics) provides ${\sim}5$pp overall lift (${\sim}18$pp on Tier~1); we report numbers both with and without it.
GPT-5.1 achieves the lowest ECE (0.107); open-weight LLMs reach 0.25--0.33, reflecting aggressive flagging.
At venue-realistic prevalence ($\pi{\approx}2\%$), $\text{PPV}\,=\,\text{DR}\cdot\pi / (\text{DR}\cdot\pi + \text{FPR}\cdot(1{-}\pi))$ drops sharply: GPT-5.1 reaches only 8.7\% PPV; aggressive models fall below 3\% despite ${\geq}87\%$ DR (\cref{app:ppv}). \emph{FPR reduction, not DR maximization, is the critical deployment metric.}

\paragraph{Cost--accuracy tradeoff.}
\label{sec:cost}
DOI-only is cheapest (1 API call) but yields only 25.6\% DR; HaRC/verify-citations are rate-limited ($<$7\% coverage); GPT-5.1 reaches $3{\times}$ the detection rate at \$0.21/entry (\cref{fig:cost} in \cref{app:figures}).

\paragraph{Fair-budget agentic comparison.}
\label{sec:agentic}
Agentic GPT-5.1 with up to five tool calls per entry---multi-source (\texttt{resolve\_doi}, \texttt{search\_crossref}, \texttt{search\_openalex}, \texttt{search\_arxiv}) or \texttt{bibtex-updater} as a tool---lifts DR from 0.797 to 0.956--0.965 (matching BTU's 0.946) but inflates FPR from 0.171 to ${\approx}0.46$ (absence of evidence read as fabrication); F1 falls below zero-shot.
BTU-as-tool slightly dominates multi-source (ECE 0.113 vs.\ 0.165): a distilled upstream verdict is easier to interpret than raw API responses.

\paragraph{Infeasibility of HaRC even with a paid Semantic Scholar key.}
\label{sec:harc_feasibility}
Re-running HaRC with an authenticated S2 key (1 RPS, 5-hour budget) leaves 0/1119 entries actually checked by \texttt{harcx}: ${\sim}90$\,s per-entry latency (DBLP/Google Scholar fallbacks that bypass S2) exceeds the 30-min per-batch timeout. The ``full-coverage'' run reflects pre-screening alone (DR 0.209), so HaRC is not operationally feasible at benchmark scale.

\paragraph{Synthetic vs.\ real-world representativeness.}
\label{sec:synth_vs_real}
KS tests across the seven types with both real and synthetic instances show 4/7 are statistically indistinguishable ($p > 0.05$); divergent types differ primarily in author count (real 1.5--2.0 vs.\ synthetic 3.3--4.7), supporting perturbations as controlled diagnostics while motivating real-world expansion.

\paragraph{Temporal robustness.}
\label{sec:temporal_robustness}
A 448-entry supplement (300 valid 2024--2025 DBLP, 148 hallucinated; \cref{app:temporal_supplement}) shows LLM verifiers degrade sharply beyond training cutoff: GPT-5.1's FPR rises 17.1\%$\to$72.6\% ($4.2{\times}$); the five non-anomalous models collapse to F1\,${\approx}0.53$ with DR inflating to 0.846--0.986 (``flag everything unfamiliar''); DeepSeek-R1 instead routes nearly every entry to \texttt{UNCERTAIN}, yielding DR\,=\,F1\,=\,0 with FPR\,=\,0.844 (\cref{tab:temporal_supplement}).
Low-baseline-FPR models suffer the largest relative degradation ($r = -0.82$, $p = 0.02$, $n = 7$); API augmentation does not help (databases also lack recent papers).
A post-freeze probe with GPT-5.4 (training cutoff: August 2025, 11 months later than GPT-5.1's) replicates the pattern on the same 448-entry supplement: FPR drops from 74.2\% to 41.3\% as entries cross the new cutoff line, but remains far from zero even for papers GPT-5.4 should recognise---confirming that training-cutoff blindness is not an artefact of any single model generation (\cref{app:gpt54-probe}).
Two post-freeze Anthropic models probed via OpenRouter break the pattern entirely: Claude Sonnet~4.6 and Opus~4.7 hold FPR at 12.0\% and 7.3\% on the same supplement (vs.\ 41.3\% for GPT-5.4 and 57.5--78.5\% for the original cohort), with F1 at 0.793 and 0.768 (MCC 0.69 and 0.67); their dev$\to$temporal FPR shifts are only $+2.5$pp and $+1.3$pp, an order of magnitude below the original cohort's $+47$--$56$pp. The ``flag everything unfamiliar'' failure mode is therefore a behavioural pattern of certain training pipelines, not a structural property of LLM citation verification.

\paragraph{Failure modes.}
\label{sec:failure}
API tools fail on venue-level hallucinations (\texttt{preprint\_as\_published}, \texttt{wrong\_venue}) because bibliographic APIs do not distinguish venue publication from arXiv availability.
GPT-5.1 handles these (83--84\%) but struggles with \texttt{author\_mismatch} and \texttt{near\_miss\_title} (both 63\%).
Combining bibtex-updater output with GPT-5.1 nearly halves calibration error (ECE: 0.107$\to$0.086) at the cost of ${\sim}3$pp DR (81.8\% vs.\ 79.7\%)---the strongest option when calibration matters more than raw recall (\cref{app:codesign}).

\paragraph{Water-filling and factor structure.}
\label{sec:water_filling}
Benchmark optimization rewards easy subtasks~\citep{hardt2025benchmarks}: API tools concentrate on Tier~1 (Tier~1/3 ratio $>$30$\times$, Gini\,=\,0.65); LLMs perform near-uniformly (Gini\,$<$\,0.05), so we report Tier~3 F1 alongside the aggregate.
PCA on the tool$\,\times\,$type detection-rate matrix (\cref{app:factor_analysis}) separates API-vs-LLM along PC1, with recall--precision tradeoffs and tier-specific strengths on subsequent components---indicating the tiered design adds orthogonal signal beyond a single factor.
