\section{Conclusion}
\label{sec:conclusion}

Citation hallucination is a growing threat to scientific integrity.
We contribute \textsc{Hallmark}, the first benchmark focusing specifically on BibTeX metadata integrity verification: 14 hallucination types across 3 difficulty tiers, 2,525 annotated entries with 6 sub-tests each, tier-weighted metrics (rewarding detection of hard hallucinations), calibration assessment via ECE (measuring confidence accuracy), and Plackett-Luce ranking as infrastructure for future denser evaluations (mean-score ranking serves as the primary comparison given current sparse tool coverage).

Our evaluation of seven full-coverage tools reveals a stark capability gap: DOI-only detects 26\% of hallucinations while LLMs achieve 48--88\%.
Two dedicated multi-source tools (HaRC, verify-citations) were rate-limited to ${<}7\%$ coverage, preventing assessment of their detection quality but highlighting the infrastructure challenge facing API-based verification at scale.
Zero-shot LLM verifiers achieve 48--88\% detection rates---demonstrating that language models can identify the very hallucinations they produce, with a pronounced recall--precision spectrum across six LLMs from conservative (Gemini~2.5~Flash: 48\% DR, 10\% FPR) to aggressive (DeepSeek-V3.2: 88\% DR, 73\% FPR).
No single tool covers all 14 types, and venue-level hallucinations remain a blind spot where bibliographic APIs lack structured data, providing concrete targets for both tool developers and database maintainers.
A 480-entry temporal supplement confirms that this parametric verification breaks down sharply on papers beyond training cutoffs---FPR rises $4{\times}$ and F1 collapses to near-chance-level---establishing temporal robustness as a first-order deployment concern.

\textsc{Hallmark} is designed to grow: its community contribution system, temporal segmentation, and atomic evaluation design ensure that new entries and tools can be incorporated without invalidating prior results.
We release the full benchmark and evaluation infrastructure as open-source software to support continued progress on this critical problem.
